|

### 2024-12-24 paper/manuscript.Rmd
ugh, what is even APC?

Using simulations and empirical case studies, we show that it is indeed possible to provide plausible scenarios as to which generative models are more likely to have produced empirical observations, even though a reliable identification of *who* changed occurs only under very narrow conditions. In doing this, we build on the "Approximate Bayesian Computation" (APC) literature [@beaumont2010] and provide a simple grid-search procedure to help social researchers in evaluating the extent to which their target estimates might be generalized to the population of their studies. Using this procedure, we show that it is possible to approximate to the underlying data generation processes for *rate of change*, *strength of change*, and *direction of change* in a panel data. We provide an R package, `gridsearch`, to help researchers in implementing this procedure in their own work.

@@

We build on the Approximate Bayesian Computation (APC) literature [@beaumont2010] and propose a grid-search procedure to answer our research questions. The APC approach involves simulating parameter values given the data and evaluating the distribution of these parameters that potentially generated our observations. We build a rejection sampler algorithm that

>>>>

Using simulations and empirical case studies, we show that it is indeed possible to provide plausible scenarios as to which generative models are more likely to have produced empirical observations, even though a reliable identification of *who* changed occurs only under very narrow conditions. In doing this, we build on the "Approximate Bayesian Computation" (ABC) literature [@beaumont2010] and provide a simple grid-search procedure to help social researchers in evaluating the extent to which their target estimates might be generalized to the population of their studies. Using this procedure, we show that it is possible to approximate to the underlying data generation processes for *rate of change*, *strength of change*, and *direction of change* in a panel data. We provide an R package, `gridsearch`, to help researchers in implementing this procedure in their own work.

@@

We build on the Approximate Bayesian Computation (ABC) literature [@beaumont2010] and propose a grid-search procedure to answer our research questions. The ABC approach involves simulating parameter values given the data and evaluating the distribution of these parameters that potentially generated our observations. We build a rejection sampler algorithm that
